---
title: "2022 Bet Log"
author: "Sean Boren"
date: '2022-03-03'
categories: []
featured: no
image:
  caption: ''
  focal_point: ''
  preview_only: no
lastmod: '2022-03-03T13:48:45-06:00'
projects: []
slug: bet-log
subtitle: ''
summary: ''
tags: []
authors: []
---


```{r, echo=FALSE, warning=FALSE, message=FALSE,results='hide'}
bet_df <- readr::read_csv("bet_log.csv")
```

There are various approaches to modeling events and every predictive model will have its strengths 
and weaknesses. I've recognized that the current iteration of my model has some major weaknesses, 
but I've also found that it is profitable in single round head-to-head matchups when backtesting. 
From a wagering perspective, that is really all we care about; consistently profiting. 
While I intend to refine the model that produces the +EV plays for each round, I also plan on 
moving forward with this iteration for wagering purposes. 

For transparency, I will provide all of the wagers and outcomes for anything greater than 5% 
positive expected value and the results will be against the closing number at Draftkings Sportsbook.

If you look through the results, you'll notice some bias in the model. It tends to bet on/against 
certain individuals which is something you should keep in mind week over week if you are using 
my +EV matchups to make a wager. 


<div align="center">

```{r, warning=FALSE, message=FALSE, echo = FALSE}
library(reactable)
library(reactablefmtr)
library(dplyr)
reactable(select(bet_df, -outcome), 
          class = "table",
          pagination = FALSE, highlight = TRUE, striped = TRUE, 
          theme = reactableTheme(cellStyle = list(display = "flex", flexDirection = "column", justifyContent = "center")),
          groupBy = "event_name",
          defaultColDef = colDef(headerStyle = list(`border-bottom` = "solid", 
                                                               fontFamily = "Josefin Sans, sans-serif",
                                                               fontSize = "14px")),
          style = list(fontFamily = "Josefin Sans, sans-serif", fontSize = "12px", maxWidth = 1225),
          columns = list(
            event_name = colDef(name = "Event", maxWidth = 325, 
                                 style = list(position = "sticky", left = 0, zIndex = 1),
      headerStyle = list(position = "sticky", left = 0, zIndex = 1, background = "#fff",
                         `border-bottom` = "solid")
            ),
            bet_type = colDef("Bet Type", maxWidth = 100),
            pick = colDef("Pick", maxWidth = 225, 
                          style = list(borderLeft = "2px solid rgba(236, 236, 236, 1)")),
            pick_ev = colDef("EV", format = colFormat(percent = TRUE, digits = 1), maxWidth = 75),
            opponent = colDef("Opponent", maxWidth = 225,
                              style = list(borderLeft = "2px solid rgba(236, 236, 236, 1)")),
            opponent_ev = colDef("EV", format = colFormat(percent = TRUE, digits = 1), align = "center", maxWidth = 75),
            #outcome = colDef("Outcome", align = "center", maxWidth = 100),
            risk_amount = colDef("Risk", align = "center", maxWidth = 50,
                                 style = list(borderLeft = "2px solid rgba(236, 236, 236, 1)")),
            win_amount = colDef("Win", align = "center", maxWidth = 50),
            bet_result = colDef("Result", align = "center", maxWidth = 60, aggregate = "sum",
                                cell = function(value) {
                                  if (value >= 0) paste0("+", value) else value
                                },
                                style = JS("function(rowInfo) {
                                            const value = rowInfo.row['bet_result']
                                            let color
                                            if (value > 0) {
                                              color = '#008000'
                                            } else if (value < 0) {
                                              color = '#e00000'
                                            } else {
                                              color = '#777'
                                            }
                                            
                                            return { color: color, fontWeight: 'bold' }
                                           }"))),
          
          # columnGroups = list(
          #   colGroup(name = "Wagered On", columns = c("pick","pick_odds","pick_ev")),
          #   colGroup(name = "Wagered Against", columns = c("opponent","opponent_odds","opponent_ev"))
          # ),
          
          rowStyle = function(index) {
            if(bet_df[index, "bet_result"] > 0) {
              list(background = "#D0E5C9")
            } else {
              list(background = "#FFD0C3")
            }
          }
          )

htmltools::tags$link(
  href = "https://fonts.googleapis.com/css2?family=Josefin+Sans&display=swap", 
  rel = "stylesheet")

```
</div>


